Sketch Recogniton using Particle Swarm Algorithm

### 2009-04-22 draft/ChapterIntroduction.tex
aftetr my change

\begin{center}
		\includegraphics[scale=0.8]{../../neededfiles/Figures/strokeinterpolation.eps}
	\caption[Segmentation Error]{Different ways for segmenting a stroke drawn by user. a) The stroke users draw b)interpretation as two line segments c) interpretation as an arc.}
	%The figure shows an arc that the user draw which can be segmented in different ways as a single line or as an arc where a) The stroke users draw  b)interpretation as a single line segment b) interpretation as an arc.}
	\label{fig:strokeinterpolation}
\end{center}
\end{figure}

@@

The ambiguities in sketch understanding are found at many levels in the system. Firstly, in the segmentation phase, a single stroke can be interpreted as an ellipse or as a circle. Symbol ambiguity is another problem as a symbol can have more than one interpolation. Due to the user's sloppy drawing the symbols can have more than one interpolation which varies with the domain drawn in it. A similar problem was faced in handwriting recognition (Figure \ref{fig:VorU}). The problem could be solved by providing context or domain information which could not be provided in most sketches. 
\begin{figure}	
	\centering
		\includegraphics[scale=0.85]{../../neededfiles/Figures/VorU.eps}
	\caption[Handwriting Ambiguities] { The same letter can be interpreted differently in various contexts; first as V in drive or as U in Cut}
\label{fig:VorU}
\end{figure}

>>>>

\begin{center}
		\includegraphics[scale=0.8]{../../neededfiles/Figures/strokeinterpolation.eps}
	\caption[Segmentation Error]{Different ways for segmenting a stroke drawn by user. a) The stroke users draw b)interpretation as two line segments c) interpretation as an arc. This example is adapted from \cite{earlyprocess}}
	%The figure shows an arc that the user draw which can be segmented in different ways as a single line or as an arc where a) The stroke users draw  b)interpretation as a single line segment b) interpretation as an arc.}
	\label{fig:strokeinterpolation}
\end{center}
\end{figure}

@@

The ambiguities in sketch understanding are found at many levels in the system. Firstly, in the segmentation phase, a single stroke can be interpreted as an ellipse or as a circle. Symbol ambiguity is another problem as a symbol can have more than one interpolation. Due to the user's sloppy drawing the symbols can have more than one interpolation which varies with the domain drawn in it. A similar problem was faced in handwriting recognition (Figure \ref{fig:VorU}). The problem could be solved by providing context or domain information which could not be provided in most sketches. 
\begin{figure}	
	\centering
		\includegraphics[scale=0.85]{../../neededfiles/Figures/VorU.eps}
	\caption[Handwriting Ambiguities] { The same letter can be interpreted differently in various contexts; first as V in drive or as U in Cut. This example is adapted from \cite{Ambiguity}.}
\label{fig:VorU}
\end{figure}
